A Global Optimization Algorithm for Non-Convex Mixed-Integer Problems

### 2018-04-19 2018/LION_Mixed-Integer/LION2018.tex
Camera-ready version

As an illustration, in Fig. \ref{fig:1} presents the plots of the functions corresponding to a 
problem with one continuous parameter and one binary parameter.

@@

Applying the global search algorithm to solving the problem (\ref{problem_is1}), we will find 
the solution of the problem (\ref{problem_i}). In this case the major part of trials will conducted in 
the subproblem, the solving of which corresponds to the solving of the initial 
problem (\ref{problem_i}). In the rest subproblems, a minor part of trials only will be performed 
since the solutions of these subproblems are the locally optimal ones.
%with respect to the solution of the $s$-th subproblem. 
All the above is confirmed by Fig. \ref{fig:1}, where the  
points of trials executed in the course of solving this problem are denoted by the dashes.

Thus,  we have constructed the \textit{Mixed-Integer Global Search Algorithm} (MIGSA) based on the  
reduction of the MINLP to the NLP. 
%It is possible to prove that the convergence conditions for this algorithm will follow from the convergence conditions of its prototype (GSA).

@@

Let us compare the proposed MIGSA method with a genetic algorithm for solving the mixed-integer optimization problems implemented in Matlab Global Optimization Toolbox. In Table 
\ref{tab:1}, the numbers of trials required for solving the known test mixed-integer 
problems by these methods are presented. For both methods, the same accuracy of search $10^{-2}$ were used. All numerical experiments were conducted on a 
computer with Intel Core i5-7300 2.5 GHz processor and 8 Gb RAM under MS Windows 10. The 
results of experiments have demonstrated the advantage to the MIGSA method in the number 
of iterations as well as in the execution time.

@@

\bibitem{Strongin2000}
Strongin, R.G., Sergeyev, Y.D.: Global Optimization with Non-Convex Constraints. Sequential and Parallel Algorithms. Kluwer Academic Publishers, Dordrecht (2000) %; DOI: 10.1007/978-1-4615-4677-1

@@

\bibitem{Floudas}
Floudas, C.A., Pardalos, P.M.:  Handbook of Test Problems in Local and Global Optimization. Springer (1999)  %; DOI: 10.1007/978-1-4757-3040-1

@@

\bibitem{Lebedev2015}
Lebedev, I., Gergel, V.: Heterogeneous Parallel Computations for Solving Global Optimization Problems. Procedia Computer Science \textbf{66}, 53--62 (2015)

\bibitem{Gergel2015}
Gergel, V., Sidorov, S.: A Two-Level Parallel Global Search Algorithm for Solution of Computationally Intensive Multiextremal Optimization Problems. Lecture Notes in Computer Science  \textbf{9251}, 505--515 (2015)

>>>>

As an illustration, Fig. \ref{fig:1} presents the plots of the functions corresponding to a 
problem with one continuous parameter and one binary parameter.

@@

Applying the global search algorithm to solving the problem (\ref{problem_is1}), we will find 
the solution of the problem (\ref{problem_i}). In this case the major part of trials will conducted in 
the subproblem, the solving of which corresponds to the solving of the initial 
problem (\ref{problem_i}). In the rest subproblems, a only minor part of trials will be performed 
since the solutions of these subproblems are the locally optimal ones.
%with respect to the solution of the $s$-th subproblem. 
All the above is confirmed by Fig. \ref{fig:1}, where the  
points of trials executed in the course of solving this problem are denoted by the dashes.

Thus, we have constructed the \textit{Mixed-Integer Global Search Algorithm} (MIGSA) based on the  
reduction of the mixed-integer non-convex optimization problem to the non-convex optimization problem. 
%It is possible to prove that the convergence conditions for this algorithm will follow from the convergence conditions of its prototype (GSA).

@@

Let us compare the proposed MIGSA method with a genetic algorithm for solving the mixed-integer optimization problems implemented in Matlab Global Optimization Toolbox \cite{Matlab}. In Table 
\ref{tab:1}, the numbers of trials required for solving the known test mixed-integer 
problems by these methods are presented. For both methods, the same accuracy of search $10^{-2}$ were used. All numerical experiments were conducted on a 
computer with Intel Core i5-7300 2.5 GHz processor and 8 Gb RAM under MS Windows 10. The 
results of experiments have demonstrated the advantage to the MIGSA method in the number 
of iterations as well as in the execution time.

@@

\bibitem{Strongin2000}
Strongin, R.G., Sergeyev, Y.D.: Global optimization with non-convex constraints. Sequential and parallel algorithms. Kluwer Academic Publishers, Dordrecht (2000) %; DOI: 10.1007/978-1-4615-4677-1

@@

\bibitem{Floudas}
Floudas, C.A., Pardalos, P.M.:  Handbook of test problems in local and global optimization. Springer (1999)  %; DOI: 10.1007/978-1-4757-3040-1

\bibitem{Matlab}
https://www.mathworks.com/help/gads/mixed-integer-optimization.html

@@

\bibitem{Lebedev2015}
Lebedev, I., Gergel, V.: Heterogeneous parallel computations for solving global optimization problems. Procedia Computer Science \textbf{66}, 53--62 (2015)

\bibitem{Gergel2015}
Gergel, V., Sidorov, S.: A two-level parallel global search algorithm for solution of computationally intensive multiextremal optimization problems. Lecture Notes in Computer Science  \textbf{9251}, 505--515 (2015)
